%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic \& Volunteer Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Owl Monkey Project} % Organization
    {Formosa, Argentina} % Location
    {Nov. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed by Eduardo Fernandez-Duque, Yale University}
        \item{Demographic, behavioural, and biological data collection of \textit{Aotus azarae} including animal captures}
        \item{Working with sensor technology including radio telemetry, camera traps, and passive acoustic monitoring}
        \item{Analysis of bioacoustic data with experimental machine learning algorithms, and development of an open \\ source library for analysis of passive acoustic data (\entrylinkstyle{\href{https://github.com/joshseltzer/pyPAM}{pyPAM})}}
        \item{Development of an unsupervised machine learning pipeline for learning to detect animal vocalizations and \\ sounds by integrating passive acoustic monitoring with camera traps (\textbf{camPAM})}
        \item{Grant and research proposal writing (e.g. Azure Compute Credit Grant)}
      \end{cvitems}
    }
    {owlmonkeyproject.wordpress.com}

%---------------------------------------------------------
  \cventry
    {Secondary Reviewer} % Job title
    {EMNLP-IJCNLP 2019} % Organization
    {Hong Kong} % Location
    {Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted Pablo Duboue in the peer review of natural language processing papers}
      \end{cvitems}
    }
    {emnlp-ijcnlp2019.org}

%---------------------------------------------------------
  \cventry
    {Volunteer} % Job title
    {Organización para los Nativos y la Conservación de la Amazonia} % Organization
    {Beni Department, Bolivia} % Location
    {Jan. 2018 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed by Andrés Jiménez Gómez}
        \item{Rehabilitating and administering medicine to semi-captive animals \\ (\textit{Cebus apella}, \textit{Ateles chemek}, \textit{Saimiri boliviensis}, \textit{Aotus azarae}, and \textit{Nasua nasua})}
        \item{Helping coordinate a rotating roster of volunteers}
        \item{Constructing and fixing infrastructure for the park}
        \item{Maintaining and cleaning animal and human premises}
      \end{cvitems}
    }
    {oncaorg.org}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Consciousness \& Wisdom Studies Lab} % Organization
    {University of Toronto} % Location
    {Jan. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed by John Vervaeke and Anderson Todd, University of Toronto}
        \item{Designing, implementing, and deploying online experiment pipelines}
        \item{Enforcing rigorous, secure, and confidential data management practices}
        \item{Spearheading an original project (\textit{Cognitive mechanisms of growth mindsets})}
        \item{Led experimental design, logistic organization, grant applications, etc.}
      \end{cvitems}
    }
    {cwsl.ca}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Mack Lab} % Organization
    {University of Toronto} % Location
    {Mar. 2017 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed by Michael Mack, University of Toronto}
        \item{Helped conduct fMRI imaging sessions (certified as Level I fMRI Personnel)}
        \item{Assisted with computational models of memory, attention, and other topics in cognitive neuroscience}
      \end{cvitems}
    }
    {macklab.utoronto.ca}


%---------------------------------------------------------
\end{cventries}
